% shtthesis, an unofficial LaTeX thesis template for ShanghaiTech University.
% Copyright (C) 2022 Li Rundong <rundong.001@gmail.com>
%
% This program is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <https://www.gnu.org/licenses/>

% graduate setup
\documentclass[doctor]{shtthesis}
\shtsetup{
  degree-name = {工学博士},
  degree-name* = {Doctor~of~Philosophy},
  %secret-level = {白给},
  title = {用于复杂流固耦合的高性能介观流体仿真方法},
  title* = {High performance mesoscopic method for fluid\\simulation with complex fluid-solid coupling},
  keywords = {高性能流体仿真，格子玻尔兹曼方法，流固耦合，碰撞模型，边界处理，GPU优化，并行计算，自动化前处理，流体数据渲染与可视化},
  keywords* = {High-performance Fluid Simulation，Lattice Boltzmann Method，Fluid-solid Coupling, Collision Model, Boundary Treament, GPU Optimization, Parallel Computing, Automatic Preprocessing, Fluid Data Rendering and Visualization},
  author = {吕超阳},
  author* = {Lyu~Chaoyang},
  institution = {上海科技大学信息科学与技术学院},
  institution* = {School~of~Information~Science~and~Technology\\%
                  ShanghaiTech~University},
  supervisor = {刘晓培~副教授},
  supervisor* = {Professor~Liu~Xiaopei},
  %supervisor-institution = {上海科技大学信息科学与技术学院},
  discipline-level-1 = {计算机科学与技术},
  discipline-level-1* = {Computer~Science~and~Technology},
  date = {2023~年~12~月},
  date* = {December,~2023},
  bib-resource = {reference.bib},
}

% undergraduate setup
% \documentclass[bachelor, comfort]{shtthesis}
% \shtsetup{
%   title = {\ShtThesis{}~v\version{}\\使用说明},
%   title* = {A~User's~Guide~to\\\ShtThesis{}~v\version{}},
%   keywords = {上海科技大学，学位论文，\LaTeX{}},
%   keywords* = {ShanghaiTech~University, Thesis, \LaTeX{}},
%   date = {2021~年~02~月},
%   date* = {02~/~2021},
%   author = {李润东},
%   author* = {Rundong~Li},
%   author-id = {36273800},
%   entrance-year = {2017},
%   institution = {信息科学与技术学院},
%   institution* = {School~of~Information~Science~and~Technology},
%   supervisor = {范睿},
%   supervisor* = {Rui~Fan},
%   discipline = {计算机科学与技术},
%   discipline* = {Computer~Science~and~Technology},
%   bib-resource = {reference.bib},
% }

% `latex' and `shell' environments are adapted from `thuthesis'
\usepackage{listings}
\newcommand\prompt{\textup{\$}}
\lstdefinestyle{lstStyleBase}{%
  basicstyle=\small\ttfamily,
  aboveskip=\medskipamount,
  belowskip=\medskipamount,
  lineskip=0pt,
  boxpos=c,
  showlines=false,
  extendedchars=true,
  upquote=true,
  tabsize=2,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  numbers=none,
  linewidth=\linewidth,
  xleftmargin=4pt,
  xrightmargin=0pt,
  resetmargins=false,
  breaklines=true,
  breakatwhitespace=false,
  breakindent=0pt,
  breakautoindent=true,
  columns=flexible,
  keepspaces=true,
  gobble=0,
  framesep=3pt,
  rulesep=1pt,
  framerule=1pt,
  frame=l,
  rulecolor=\color{ShtRed},
  backgroundcolor=\color{gray!5},
  stringstyle=\color{green!40!black!100},
  keywordstyle=\bfseries\color{blue!50!black},
  commentstyle=\slshape\color{black!60},
  escapeinside={`'},
}
\lstdefinestyle{lstStyleShell}{%
  style=lstStyleBase,
  language=bash}
\lstdefinestyle{lstStyleLaTeX}{%
  style=lstStyleBase,
  language=[LaTeX]TeX}
\lstnewenvironment{latex}{\lstset{style=lstStyleLaTeX}}{}
\lstnewenvironment{shell}{\lstset{style=lstStyleShell}}{}

\providecommand{\TODO}[1]{{\color{red}{#1}}}

\usepackage{hologo}
\ifluahbtex
  \usepackage{emoji}
\else
  \providecommand{\emoji}[1]{ \fbox{\emph{#1}} }
\fi

\usepackage{subcaption}
\usepackage{ctable}
\usepackage[list=off]{bicaption}
\usepackage{lipsum}
\captionsetup[figure][bi-second]{name=Figure}
\captionsetup[table][bi-second]{name=Table}

\makeatletter
  \def\ifundergraduate{\ifsht@undergraduate}
  \def\ifgraduate{\ifsht@graduate}
\makeatother

\newcommand{\citepen}[1]{{\defcounter{gbcitelocalcase}{2}\citep{#1}}}
\newcommand{\citeten}[1]{{\defcounter{gbcitelocalcase}{2}\citet{#1}}}

\begin{document}

\maketitle

\frontmatter
% A - 中英文摘要
\input{contents/a_abstract}

\makeindices

\ifgraduate
% B - 符号列表
\input{contents/b_nomenclatures}
\fi

\mainmatter
% C - 正文
\input{contents/c1_introduction}
\input{contents/c2_background}
\input{contents/c3_cg_boundary}
\input{contents/c4_auto_boundary}
\input{contents/c5_caa}
\input{contents/c6_results}
\input{contents/c7_conclusion}

\makebiblio

\backmatter
\input{contents/d_acknowledgement}

\ifgraduate
\begin{resume}
  吕超阳，男，1996年4月生，河南郑州人。

  2014年9月——2018年6月，就读于哈尔滨工业大学 (威海) 软件学院，并获得工学学士学位。

  2018年9月——2024年1月，在上海科技大学信息科学与技术学院攻读工学博士学位。  
\end{resume}

\begin{publications}
  \begin{enumerate}
    \item Lyu Chaoyang, Li Wei, Desbrun Mathieu, et al. Fast and versatile fluid-solid coupling for turbulent flow simulation[J]. ACM Transactions on Graphics, 2021, 40(6): Article 201. (中国计算机学会推荐国际学术期刊A类；该文汇报于SIGGRAPH Asia 2021，该会议为中国计算机学会推荐国际学术会议A类)
    \item Lyu Chaoyang, Bai Kai, Wu Yiheng, et al. Building a virtual weakly-compressible wind tunnel testing facility[J]. ACM Transactions on Graphics, 2023, 42(4): Article 125. (中国计算机学会推荐国际学术期刊A类；该文汇报于SIGGRAPH 2023，该会议为中国计算机学会推荐国际学术会议A类)
  \end{enumerate}
\end{publications}

\begin{publications*}
  \begin{enumerate}
    \item ACM Transactions on Graphics, 2021. (发表于SIGGRAPH Asia 2021，中国计算机学会推荐国际学术会议A类，本文作者为第一作者)
    \item ACM Transactions on Graphics, 2023. (发表于SIGGRAPH 2023，中国计算机学会推荐国际学术会议A类，本文作者为第一作者)
  \end{enumerate}
\end{publications*}

% \begin{patents}
%   无。
% \end{patents}

% \begin{patents*}
%   无。
% \end{patents*}

% \begin{projects}
%   个人参与的科研项目、获奖情况…… （仅非匿名环境显示）
% \end{projects}
\fi

\end{document}
